### 2015-07-20 src/misc/s6_thanks.tex
Marja and Wim in bold.

As with everything in life, writing this thesis was not always easy. Thanks to \textbf{Daphne} and my parents, \textbf{Marja and Wim}, for their unconditional support and confidence in me while I was writing this thesis.

>>>>

As with everything in life, writing this thesis was not always easy. Thanks to \textbf{Daphne} and my parents, \textbf{Marja} and \textbf{Wim}, for their unconditional support and confidence in me while I was writing this thesis.
